### 2016-10-16 p01-ch01-2012/paper.tex
Fix spacing issues

%\Mahdi{Do we want to talk about with clauses?}

@@

\begin{lstlisting}[float=t, label=ch01:lst:exres, caption=Exclusive Resource in Creol]
interface Resource begin
	(* \label{ch01:lst:priority_range} *)(*
	%with User  \label{ch01:lst:with} 
	*)
		op request()
		op release()
end

@@

\begin{lstlisting}[frame=none, numbers=none]
priority range 0..9
\end{lstlisting}

@@

\begin{lstlisting}[frame=none, numbers=none]
mutex ! request() priority(7);
\end{lstlisting}

@@

\begin{lstlisting}[frame=none, numbers=none]
op request() priority(2) == ...
op release() priority(0) == ...
\end{lstlisting}

@@

\begin{lstlisting}[frame=none, numbers=none]
await (*$\sim$*)taken priority(1);
\end{lstlisting}

@@

For example, in {\ftt{ExclusiveResource}}, we have two different levels of priorities, namely  the client-side and server-side priorities, which range over $P_1 = \{0, \ldots, 9\}$ and $P_2 = \{0, 1, 2\}$, respectively. 
So, we define $\delta: P_1 \times P_2 \rightarrow P$ as:
%
\[
\delta(p_1, p_2) = p_1 + p_2 \times |P_1|
\]

>>>>

@@

\begin{lstlisting}[float=t, label=ch01:lst:exres, caption=Exclusive Resource in Creol]
interface Resource begin (* \label{ch01:lst:priority_range} *)
		op request()
		op release()
end

@@

\begin{quote}
\lstinline{priority range 0..9}
\end{quote}

@@

\begin{quote}
\lstinline{mutex ! request() priority(7);}
\end{quote}

@@

\begin{quote}
\lstinline{op request() priority(2) == ...}\\
\lstinline{op release() priority(0) == ...}
\end{quote}

@@

\begin{quote}
\lstinline{await ~taken priority(1);}
\end{quote}

@@

For example, in {\ftt{ExclusiveResource}}, we have two different levels of priorities, namely  the client-side and server-side priorities, which range over $P_1 = \{0, \ldots, 9\}$ and $P_2 = \{0, 1, 2\}$, respectively. 
So, we define $\delta: P_1 \times P_2 \rightarrow P$ as:

\[
\delta(p_1, p_2) = p_1 + p_2 \times |P_1|
\]
